CMPEN/EE 454 Project 2 Report

### 2015-12-12 p2/report/project_report.tex
intermediate output for harris

\section{Intermediate Results}
In this section we include results from the various modules implemented in this program.  These results were used to verify correctness of each particular unit of code, as well as tune the entire program to produce accurate results.
\subsection{Harris Corner Detection}
To test our implementation of the Harris Corner Detection algorithm, we used various images containing geometric scenes.  For example, below is a skyscraper facade passed through our routine.  As expected, the corner points on each window have very high intensity values and the edges in the image have very low intensity values.
\begin{center}
\fbox{\includegraphics[width=150pt, height=150pt]{harrisinput}}
\fbox{\includegraphics[width=150pt, height=150pt]{harrisoutput}}
\end{center}

>>>>

\section{Intermediate Results}
In this section we include results from the various modules implemented in this program.  These results were used to verify correctness of each particular unit of code, as well as tune the entire program to produce accurate results.
\subsection{Harris Corner Detection}
To test our implementation of the Harris Corner Detection algorithm, we used various images containing geometric scenes.  For example, below is a skyscraper facade passed through our routine.  As expected, the corner points on each window have very high intensity values and the edges in the image have very low intensity values.
\begin{center}
\fbox{\includegraphics[width=150pt, height=150pt]{harrisinput}}
\fbox{\includegraphics[width=150pt, height=150pt]{harrisoutput}}
\end{center}
~\\
This window image is very idealistic; the corners in this image are distinctive and well-defined.  We have found that this corner detection algorithm also works well on less-ideal input.  Here is the result when the algorithm is run on the first bounding box in the image 7022:
\begin{center}
\fbox{\includegraphics[scale=.4]{woman}}
\fbox{\includegraphics[scale=.4]{womanharris}}
\end{center}
The algorithm does a good job of suppressing the uniform regions of the image (the woman's jacket, shirt, and pants) and highlights regions of high contrast (the woman's hand against her jacket, hair against her head).
